Inverse conformational selection in lipid-protein binding

### 2021-07-28 manuscriptPGPE.tex
update pdfs

  % Put your acknowledgments here.
M.J. thanks CSC -- IT Center for Science for computational resources and the Emil Aaltonen foundation for financial support.
T.M.F. was supported by the Ministry of Economics, Science
and Digitalisation of the State of Saxony-Anhalt, Germany.
P.B. was supported by the Academy of Finland (Grant 311031).
F.F.-R. acknowledges Tecnol\'{o}gico Nacional de M\'{e}xico Proyecto IT16C431, Direcci\'{o}n General de Asuntos del Personal Acad\'{e}mico (DGAPA) Programa de Apoyo a Proyectos de Investigaci\'{o}n e Innovaci\'{o}n Tecnol\'{o}gica (PAPIIT) IG100920, CONACyT Ciencia de Frontera 74884 for financial support and Miztli-Direcci\'{o}n de C\'{o}mputo y de Tecnolog\'{i}as de Informaci\'{o}n y Comunicaci\'{o}n (DGTIC) - Universidad Nacional Aut\'{o}noma de M{\'e}xico (UNAM) (Project LANCAD-UNAM-DGTIC-057) facilities for computing-time allocation.
I.G. was supported by the Ministry of Science and Higher Education of the Russian Federation (agreement \#075-00337-20-03, project FSMG-2020-0003). 
J.J.M. gratefully acknowledges financial support from the Carlsberg 
Foundation in the form of a postdoctoral fellowship while at 
the University of Chicago (grants CF15-0552, CF16-0639, and 
CF17-0783) and the research framework provided by the 
Research Computing Center at the University of Chicago.
O.H.S.O, A.M.K, and S.I.V acknowledge CSC -- IT Center for Science for computational resources and Academy of Finland (grants 315596 and 319902) for financial support.
T.J.P. acknowledges use of the Iridis high-performance computing resources at the University of Southampton.
J.M. thanks the Center for Information Technology of the University of Groningen for their support and for providing access to the Peregrine high performance computing cluster. R.G.-F. and A. P. acknowledge the financial support from Fundação para a Ciência e Tecnologia (FCT) and FEDER European funds, through the project PTDC/BIA-BFS/30579/2017 (POCI-01-0145-30579) and UIDB/00081/2020. R.G.-F. thanks Ministerio de Ciencia, Innovación y Universidades for a “Ramón y Cajal” contract (RYC-2016-20335), and also to the Spanish Agencia Estatal de Investigación (AEI) and the ERDF (RTI2018-098795-A-I00) and the Xunta de Galicia and the ERDF (ED431F 2020/05), and Centro singular de investigación de Galicia accreditation 2016-2019, ED431G/09). Á. P. acknowledges to the Spanish Agencia Estatal de Investigación (AEI) and the ERDF (PID2019-111327GB-I00). R.G.-F., A. P. and Á. P. acknowledge to the Centro de Supercomputación de Galicia (CESGA) for technical support and computing time.

>>>>

  % Put your acknowledgments here.
M.J. thanks CSC -- IT Center for Science for computational resources and the Emil Aaltonen foundation for financial support.
T.M.F. was supported by the Ministry of Economics, Science
and Digitalisation of the State of Saxony-Anhalt, Germany.
P.B. was supported by the Academy of Finland (Grant 311031).
F.F.-R. acknowledges Tecnol\'{o}gico Nacional de M\'{e}xico Proyecto IT16C431, Direcci\'{o}n General de Asuntos del Personal Acad\'{e}mico (DGAPA) Programa de Apoyo a Proyectos de Investigaci\'{o}n e Innovaci\'{o}n Tecnol\'{o}gica (PAPIIT) IG100920, CONACyT Ciencia de Frontera 74884 for financial support and Miztli-Direcci\'{o}n de C\'{o}mputo y de Tecnolog\'{i}as de Informaci\'{o}n y Comunicaci\'{o}n (DGTIC) - Universidad Nacional Aut\'{o}noma de M{\'e}xico (UNAM) (Project LANCAD-UNAM-DGTIC-057) facilities for computing-time allocation.
I.G. was supported by the Ministry of Science and Higher Education of the Russian Federation (agreement \#075-00337-20-03, project FSMG-2020-0003). 
J.J.M. gratefully acknowledges financial support from the Carlsberg 
Foundation in the form of a postdoctoral fellowship while at 
the University of Chicago (grants CF15-0552, CF16-0639, and 
CF17-0783) and the research framework provided by the 
Research Computing Center at the University of Chicago.
O.H.S.O, A.M.K, and S.I.V acknowledge CSC -- IT Center for Science for computational resources and Academy of Finland (grants 315596 and 319902) for financial support.
T.J.P. acknowledges use of the Iridis high-performance computing resources at the University of Southampton.
J.M. thanks the Center for Information Technology of the University of Groningen for their support and for providing access to the Peregrine high performance computing cluster. R.G.-F. and A. P. acknowledge the financial support from Funda{\c c}{\=a}o para a Ci{\^ e}ncia e Tecnologia (FCT) and FEDER European funds, through the project PTDC/BIA-BFS/30579/2017 (POCI-01-0145-30579) and UIDB/00081/2020. R.G.-F. thanks Ministerio de Ciencia, Innovaci{\'o}n y Universidades for a ''Ram{\'o}n y Cajal'' contract (RYC-2016-20335), and also to the Spanish Agencia Estatal de Investigaci{\'o}n (AEI) and the ERDF (RTI2018-098795-A-I00) and the Xunta de Galicia and the ERDF (ED431F 2020/05), and Centro singular de investigaci{\'o}n de Galicia accreditation 2016-2019, ED431G/09). {\'A}. P. acknowledges to the Spanish Agencia Estatal de Investigaci{\'o}n (AEI) and the ERDF (PID2019-111327GB-I00). R.G.-F., A. P. and {\'A}. P. acknowledge to the Centro de Supercomputaci{\'o}n de Galicia (CESGA) for technical support and computing time.
